Hydra Battles and Cie

### 2021-05-26 doc/part-hydras.tex
corrections of typos

Since the canonical sequence of $\omega$ is composed of finite ordinals, 
it is easy to get the formula associated with $H_\omega$.

@@

\item In particular, we have got a formula for $H'_{\omega^{i+1}}$.

@@

\begin{Coqsrc}
Fact F0 : H'_ (Phi0 3) 3 = f (f (f (f 3))).
 rewrite R0; reflexivity. 
Qed.
\end{Coqsrc}

@@

This number looks quite big; let us compute an approximation in \texttt{Ocaml}:

@@

But beware of non-theorems! For instance, one could believe that $H'$ is monotonous in its first argument. The following proof shows this is false.

@@

\emph{From Module~\href{../theories/html/hydras.Epsilon0.L_alpha.html}{Epsilon0.L\_alpha}}

@@

\begin{remark}
The difference with the ``classic'' Wainer hierarchy 
$f\_alpha\;(\alpha<\epsilon_0)$ lies in the second equation:
$f_{\beta+1}(i) = (f_\beta)^{(i)}(i)$ and not
$f_{\beta+1}(i) = (f_\beta)^{(i+1)}(i)$. A module about 
the classic Wainer hierarchy is in preparation.
\end{remark}

>>>>

Since the canonical sequence of $\omega$ is composed of finite ordinals, 
it is easy to get the formula associated with $H'_\omega$.

@@

\item In particular, we derive a formula for $H'_{\omega^{i+1}}$.

@@

\begin{Coqsrc}
Fact F0 : H'_ (Phi0 3) 3 = f (f (f (f 3))).
proof. rewrite R0; reflexivity. Qed.
\end{Coqsrc}

@@

This number looks quite big; let us compute an approximation with \texttt{Ocaml}:

@@

But beware of fake theorems! For instance, one could believe that $H'$ is monotonous in its first argument. The following proof shows this is false.

@@

\noindent
\emph{From Module~\href{../theories/html/hydras.Epsilon0.L_alpha.html}{Epsilon0.L\_alpha}}

@@

\begin{remark}
The difference with the ``classic'' Wainer hierarchy 
$f\_\alpha\;(\alpha<\epsilon_0)$ lies in the second equation:
$f_{\beta+1}(i) = (f_\beta)^{(i)}(i)$ and not
$f_{\beta+1}(i) = (f_\beta)^{(i+1)}(i)$. A module about 
the classic Wainer hierarchy is in preparation.
\end{remark}
